---
title: "easyphysicsR"
output: rmarkdown::html_vignette
author: UBC_MDS_Group16
vignette: >
  %\VignetteIndexEntry{easyphysicsR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


A package with useful physics formulas to make physics easy and fun for users! It uses four functions to easily calculate four classic physics theories. By making the functions concise and supporting graphs to demonstrate the theories, physics beginners might find learning physics fun and not daunting! All functions in this package require only arguments in numeric format; no dataset files are needed. easyphysics can also generate easy-to-understand visualizations to further reveal the physics effects.

The package has four functions which can provide solutions for Physics
Equations. Input will be taken from the User and the solutions will be
provided by the functions. The four functions are as follows:

- `freefall()` calculates the time it takes for a falling object using
  the equation of motion height = 1/2\*gt^2, given the height and
  gravity of the free fall. It returns the time it takes for the free
  fall, and a plot compares the time of the free fall on different
  planets with a list. The distance traveled by the falling object
  (height) and the acceleration of gravity (g, default g = 9.8) are the
  function’s arguments.
- `gravitational_energy()` calculates the energy possessed or acquired
  by an object due to a change in its position when it is present in a
  gravitational field = m*g*h
- `kinetic_energy()` calculates the Kinetic Energy of an object. When
  work is done on an object, energy is transferred, and the object moves
  with a new constant speed. We call the energy that is transferred
  kinetic energy, and it depends on the mass and speed achieved. The
  kinetic energy equation is given as: KE = 1/2*m*v^2, Where KE is the
  kinetic energy, m is the body’s mass, and v is the body’s velocity.
- `static_friction_ground()` calculates the friction force for static
  object. The formula is fr = mu \* N, where the mu is the coefficient
  of friction which incorporating the characteristics of the surface.


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(easyphysicsR)

```

```{r fig.height=4, fig.width=5}
# example usage of the freefall function
freefall(10, g = 9.8)
easyphysicsR::freefall(100, g = 15)
```
```{r}
# example usage of the gravitational_energy function
gravitational_energy(2.5,10,9.80665)
easyphysicsR::gravitational_energy(5,20,9.80665)

```

```{r}
# example usage of the kinetic_energy function 
kinetic_energy(0.6, 3)
easyphysicsR::kinetic_energy(6, 10)

```

```{r}
# example usage of the static_friction_ground function 
static_friction_ground(mu=0.2, g = 9.8, m=10)
easyphysicsR::static_friction_ground(mu=5, g = 15, m=10)

```

